Online appendix for "Dynamics of International Giving: How Heuristics Shape Individual Donor Preferences

### 2020-09-29 manuscript/manuscript.Rmd
Add all other pre R&R changes

---
title: "Dynamics of international giving: Exploring individual donor preferences"
short-title: Charity During Crackdown
author:
- name: Suparna Chaudhry
  affiliation: Lewis \& Clark College
  email: schaudhry@lclark.edu
  url: http://www.suparnachaudhry.com/
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  url: https://www.andrewheiss.com/
date: "`r format(Sys.time(), '%B %e, %Y')`"
git-repo: https://github.com/andrewheiss/ngo-crackdowns-philanthropy
reference-section-title: References
toc: false
title-page: true
abstract: >-
  State restrictions on non-governmental organizations (NGOs) have become increasingly pervasive across the globe. While this crackdown has been shown to have a negative impact on public funding flows, we know little about how it impacts private philanthropy. How does information about crackdown abroad, as well as organizational attributes of nonprofits affect individual donors’ willingness to donate internationally? Using a survey experiment, we find that learning about repressive NGO environments increases generosity in that already-likely donors are willing to donate substantially more to legally besieged nonprofits. This generosity persists when mediated by two organizational-level heuristics: NGO issue areas and main funding sources. We discuss the implications of our results on how nonprofits can use different framing appeals to increase fundraising at a time when traditional public donor funding to such organizations is decreasing. 
thanks: >-
  We thank Mark Buntaine, Michael DeCrescenzo, Jeffrey Friedman, Thomas Leeper, and Tristan Mahr for their helpful comments and input. We also thank Samantha Camilletti and Joshua Dutro for their excellent research assistance. This experiment received approval by the human subjects research committees at both Christopher Newport University (018.042) and Brigham Young University (E18104). We preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at <https://osf.io/dx973/>.
author-note: >-
  Suparna Chaudhry, PhD, Assistant Professor of International Affairs, Lewis \& Clark College; Andrew Heiss, PhD, Assistant Professor of Public Management, Andrew Young School of Policy Studies, Georgia State University. 
additional-info: Figures should appear in color online only, not in print.
correspondence: >-
  Correspondence concerning this article should be addressed to Suparna Chaudhry, PhD, Department of International Affairs, Lewis \& Clark College, 0615 SW Palatine Hill Rd. Portland, OR 97219. Contact: schaudhry@lclark.edu
word-count: "7,935"
keywords: international NGOs, donor behavior, philanthropy, human rights, repression, international giving, donor choice
---

@@

Over the last three decades, governments across the world have sought to limit the work of nonprofits and nongovernmental organizations (NGOs)—a phenomenon known as "closing civic space" [@Carothers:2015; @DPR:2016]. Repressive governments have enacted laws creating barriers to advocacy and funding for a variety of NGOs. The adverse effects of these laws are particularly felt in countries with weak institutions and poor governance. International donors directing aid to these countries typically seek out NGOs to implement their projects, as direct aid transfers to recipient governments pose the risk of misuse and bureaucratic inefficiency [@Dietrich2013]. However, official aid flows to NGOs have decreased considerably in countries with repressive NGO environments [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018]. While we know there has been a negative impact on funding from official donors, we know relatively little about how this crackdown affects private donors, in particular how it influences individual donors' willingness to donate internationally.

Charitable giving to nonprofits working in international affairs has steadily increased over the past two decades.[^internationalaffairs] Between 2014 and 2016, giving to international affairs-focused issues increased by 14.1% [@givingusa2017report]. This amount is not insignificant—by 2016, total private giving to nonprofits working in international affairs had increased to \$22.03 billion [@givingusa:2017]. Most notably, a large portion of this growth was driven by individuals making small-scale donations. In 2017, individuals gave $286.7 billion, or approximately 70% of total giving to international affairs. This further increased to \$427.71 billion in 2018, 85.7% of which was through individuals [@givingusa:2019]. While a lot is known about individuals' motivations for giving locally [@BekkersWiepking:2011], much less is known about motivations to give internationally and these large amounts show the urgency of understanding this phenomenon. What factors affect individual donor preferences on giving to international causes? How does information about repressive NGO environments abroad affect donors' willingness to donate internationally, and how does knowledge of legal crackdown interact with other organizational attributes?

@@

To measure the effect of structural and organization-level heuristics on individual donor preferences, we use an experiment to vary the different frames donors are exposed to. Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs tailor their fundraising strategies for individuals. Prior to launching the experiment, we preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at [https://osf.io/dx973/?view_only=73bf237f7f5e4e15908bc4160517ccb3](https://osf.io/dx973/?view_only=73bf237f7f5e4e15908bc4160517ccb3). The online appendix also includes the full text of the survey experiment, as well as details about our sample demographics, balance across experimental conditions, CONSORT diagram, and Bayesian priors. The analysis is fully reproducible using code and data available at ANONYMIZED.

@@

In contrast, when donors know that a human rights organization is privately funded, they are more likely to donate when there is a legal crackdown than when the NGO faces no legal hurdles (`r filter(likely, title == "Human rights | Private")$delta`; `r filter(likely, title == "Human rights | Private")$p_neq0`). As explained previously, each of the heuristics on their own influence the propensity to donate, but we do not yet know how the interaction between heuristics affects donor behavior. Here, the private funding heuristic appears to override the dampening in likelihood that should come from focusing on more contentious human rights issues. For humanitarian assistance NGOs, however, legal crackdowns do not have a significant effect on the likelihood of donation when nesting either funding and issue frames—neither of the nested experimental frames play a heuristic role.

>>>>

---
title: "Dynamics of International Giving: How Heuristics Shape Individual Donor Preferences"
short-title: Dynamics of International Giving
author:
- name: Suparna Chaudhry
  affiliation: "Lewis & Clark College"
  email: schaudhry@lclark.edu
  url: http://www.suparnachaudhry.com/
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  url: https://www.andrewheiss.com/
date: "`r format(Sys.time(), '%B %e, %Y')`"
git-repo: https://github.com/andrewheiss/ngo-crackdowns-philanthropy
reference-section-title: References
toc: false
title-page: true
abstract: >-
  State restrictions on non-governmental organizations (NGOs) have become increasingly pervasive across the globe. While this crackdown has been shown to have a negative impact on public funding flows, we know little about how it impacts private philanthropy. How does information about crackdown abroad, as well as organizational attributes of nonprofits affect individual donors’ willingness to donate internationally? Using a survey experiment, we find that learning about repressive NGO environments increases generosity in that already-likely donors are willing to donate substantially more to legally besieged nonprofits. This generosity persists when mediated by two organizational-level heuristics: NGO issue areas and main funding sources. We discuss the implications of our results on how nonprofits can use different framing appeals to increase fundraising at a time when traditional public donor funding to such organizations is decreasing. 
thanks: >-
  We thank Mark Buntaine, Michael DeCrescenzo, Jeffrey Friedman, Thomas Leeper, and Tristan Mahr for their helpful comments and input. We also thank Samantha Camilletti and Joshua Dutro for their excellent research assistance. This experiment received approval by the human subjects research committees at both Christopher Newport University (018.042) and Brigham Young University (E18104). We preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at <https://osf.io/dx973/>.
author-note: >-
  Suparna Chaudhry, PhD, Assistant Professor of International Affairs, Lewis \& Clark College; Andrew Heiss, PhD, Assistant Professor of Public Management, Andrew Young School of Policy Studies, Georgia State University. 
additional-info: Figures should appear in color online only, not in print.
correspondence: >-
  Correspondence concerning this article should be addressed to Suparna Chaudhry, PhD, Department of International Affairs, Lewis \& Clark College, 0615 SW Palatine Hill Rd. Portland, OR 97219. Contact: schaudhry@lclark.edu
word-count: "8,012"
keywords: international NGOs, donor behavior, philanthropy, human rights, repression, international giving, donor choice
---

@@

Over the last three decades, governments across the world have sought to limit the work of nonprofits and nongovernmental organizations (NGOs)—a phenomenon known as "closing civic space" [@Carothers:2015; @DPR:2016]. Repressive governments have enacted laws creating barriers to advocacy and funding for a variety of NGOs. The adverse effects of these laws are particularly felt in countries with weak institutions and poor governance. International donors directing aid to these countries typically seek out NGOs to implement their projects, as direct aid transfers to recipient governments pose the risk of misuse and bureaucratic inefficiency [@Dietrich2013]. However, official aid flows to NGOs have decreased considerably in countries that repress NGOs [@Brechenmacher:2017; @ChaudhryHeiss:2018; @DupuyPrakash:2018]. While we know there has been a negative impact on funding from official donors, we know relatively little about how this crackdown affects private donors, in particular how it influences individual donors' willingness to donate internationally.

Charitable giving to nonprofits working in international affairs has steadily increased over the past two decades.[^internationalaffairs] From 2014–2016, giving to international affairs-focused issues increased by 14.1% [@givingusa2017report]. This amount is not insignificant—by 2016, total private giving to nonprofits working in international affairs had increased to \$22.03 billion [@givingusa:2017]. Most notably, a large portion of this growth was driven by individuals making small-scale donations. In 2017, individuals gave $286.7 billion, or approximately 70% of total giving to international affairs. This further increased to \$427.71 billion in 2018, 85.7% of which was through individuals [@givingusa:2019]. While much is known about individuals' motivations for giving locally [@BekkersWiepking:2011], much less is known about motivations to give internationally. These large amounts show the urgency of understanding this phenomenon. What factors affect individual donor preferences on giving to international causes? How does information about repressive NGO environments abroad affect donors' willingness to donate internationally, and how does knowledge of legal crackdown interact with other organizational attributes?

@@

To measure the effect of structural and organization-level heuristics on individual donor preferences, we use an experiment to vary the different frames donors are exposed to. Comparing these effects allows us to measure the relative strength of these heuristics, and ultimately help NGOs tailor their fundraising strategies for individuals. Prior to launching the experiment, we preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at [https://bit.ly/osf-prereg-anon](https://bit.ly/osf-prereg-anon). The online appendix also includes the full text of the survey experiment, as well as details about our sample demographics, balance across experimental conditions, CONSORT diagram, and Bayesian priors. The analysis is fully reproducible using code and data available at ANONYMIZED.

@@

In contrast, when donors know that a human rights organization is privately funded, they are more likely to donate when there is a legal crackdown than when the NGO faces no legal hurdles (`r filter(likely, title == "Human rights | Private")$delta`; `r filter(likely, title == "Human rights | Private")$p_neq0`). As explained previously, each of the heuristics on their own influence the propensity to donate, but we do not yet know how the interaction between heuristics affects donor behavior. Here, the private funding heuristic appears to override the dampening in likelihood that should come from focusing on more contentious human rights issues. For humanitarian assistance NGOs, however, legal crackdowns do not have a significant effect on the likelihood of donation when nesting either funding or issue frames—neither of the nested experimental frames play a heuristic role.

### 2020-09-29 manuscript/supplement.Rmd
Add all other pre R&R changes

---
title: "Online appendix for Charity During Crackdown: Analyzing the Impact of State Repression of NGOs on Philanthropy"
short-title: Online appendix for Charity During Crackdown
author:
- name: Suparna Chaudhry
  affiliation: Christopher Newport University
  email: suparna.chaudhry@cnu.edu
  url: http://www.suparnachaudhry.com/
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  url: https://www.andrewheiss.com/
date: "`r format(Sys.time(), '%B %e, %Y')`"
title-page: false
published: 
git-repo: https://github.com/andrewheiss/ngo-crackdowns-philanthropy
reference-section-title: References
toc: true
appendix: true
---

@@

Prior to launching the survey, we preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at [https://osf.io/dx973/](https://osf.io/dx973/). We made two minor deviations from the original preregistration. First, in the *text* of our preregistration, we only specified the non-nested versions of our hypotheses:

@@

In our preregistered data analysis *plan*, however, we explained that we will test the interacted versions of the hypotheses (i.e. donors will give more to humanitarian NGOs facing legal crackdowns, etc.). This was an oversight—we inadvertently used overly simple (and incorrect) textual hypotheses, but correctly described the full analysis plan (using the correct, unstated, unstated hypotheses).

>>>>

---
title: 'Online appendix for "Dynamics of International Giving: How Heuristics Shape Individual Donor Preferences"'
short-title: 'Online appendix for "Dynamics of International Giving"'
author:
- name: Suparna Chaudhry
  affiliation: "Lewis & Clark College"
  email: schaudhry@lclark.edu
  url: http://www.suparnachaudhry.com/
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  url: https://www.andrewheiss.com/
date: "`r format(Sys.time(), '%B %e, %Y')`"
title-page: false
published: 
git-repo: https://github.com/andrewheiss/ngo-crackdowns-philanthropy
reference-section-title: References
toc: true
appendix: true
---

@@

Prior to launching the survey, we preregistered our hypotheses and research design at the Open Science Framework, and our preregistration protocol is available at [https://osf.io/dx973/](https://osf.io/dx973/). We made two minor deviations from the original preregistration. First, in the *text* of our preregistration, we inadvertently only specified the non-nested versions of our hypotheses:

@@

In our preregistered data analysis *plan*, however, we describe the nested and interacted versions of the hypotheses (i.e. donors will give more to humanitarian NGOs facing legal crackdowns, etc.). This was an oversight—we inadvertently used overly simple (and incorrect) textual hypotheses, but correctly described the full analysis plan (using the correct, unstated, unstated hypotheses).
